Objects preparations

### 2025-08-22 Objects_preparations.Rmd
Update for revision

con$buildGraph(ncomps = 20)
con$findCommunities()
con$embedGraph(method = "UMAP")
```

@@

@@

@@

>>>>

con$buildGraph()
con$findCommunities()
con$embedGraph(method = "largeVis", M = 30, gamma = 10)
```

@@

con_msa$n.cores <- 1
con_msa$buildGraph()
con_msa$findCommunities()
con_msa$embedGraph(method = "largeVis", M = 30, gamma = 10)

@@

con_pd$n.cores <- 1
con_pd$buildGraph()
con_pd$findCommunities()
con_pd$embedGraph(method = "largeVis", M = 30, gamma = 10)

@@

con_dis$n.cores <- 1
con_dis$buildGraph()
con_dis$findCommunities()
con_dis$embedGraph(method = "largeVis", M = 30, gamma = 10)
